Курсовая работа по теме \\ \Huge{«Методы оптимизации»}

### 2008-12-14 simplex-method.tkz.tex
Using different pattern
Antigradient direction

\begin{figure}[!thb]
  \centering
  \begin{tikzpicture}
    \begin{axis}[
      x=1.5cm, y=2cm,
      xlabel=$x_1$,
      ylabel=$x_2$,
      xtick={1, 2, 3, 4, 5, 6},
      ytick={1, 3, 4, 5},
      xmin=-2, ymin=-1,
      xmax=7, ymax=7,
      axis x line=center,
      axis y line=center,
      pattern color=gray,
      area legend]

      \addplot[draw=none,mark=none,pattern=north east lines] coordinates{
        (0,0) (0,2) (2,3.5) (5,0)} \closedcycle;
      \label{plot:simplex-feasible-space}

>>>>

\begin{figure}[!thb]
  \centering
  \begin{tikzpicture}
    \begin{axis}[
      x=1.5cm, y=1.5cm,
      xlabel=$x_1$,
      ylabel=$x_2$,
      xtick={1, 2, 3, 4, 5, 6},
      ytick={1, 3, 4, 5},
      xmin=-2, ymin=-1,
      xmax=7, ymax=7,
      axis x line=center,
      axis y line=center,
      pattern color=gray,
      area legend]

      \addplot[draw=none,mark=none,pattern=dots]
      coordinates{(0,0) (0,2) (2,3.5) (5,0)} \closedcycle;
      \label{plot:simplex-feasible-space}

      \draw[arrows=-triangle 60, dashed, ultra thick]
      (axis cs:1.5, 0.75) -- (axis cs:2.25,2.25);
      \label{plot:simplex-antigrow}
